\centerline{\huge\textbf{OpenDiabetesVault-Plot}} 
\vspace{2em}

\begin{changemargin}{4em}{4em} 

Copyright \textcopyright ~\the\year Jens Heuschkel
\vspace{1em}

This Plot was produced by the OpenDiabetes-Plotter, which is part of the OpenDiabetesVault tool suite.
For more information check the website \url{http://www.opendiabetes.de}.

This program is free software: you can redistribute it and/or modify
it under the terms of the GNU General Public License as published by
the Free Software Foundation, either version 3 of the License, or
(at your option) any later version.

This program is distributed in the hope that it will be useful,
but WITHOUT ANY WARRANTY; without even the implied warranty of
MERCHANTABILITY or FITNESS FOR A PARTICULAR PURPOSE.  See the
GNU General Public License for more details.

You should have received a copy of the GNU General Public License
along with this program.  If not, see \url{http://www.gnu.org/licenses/}.
\vspace{1em}

Contribute!
If you are interested in contributing to OpenDiabetesVault you have several ways:

Idea or code contribution: 
You are always welcome to post an idea what you would like to see as part of OpenDiabatesVault.
Please motivate your idea always with data sources (What data would you like to use for your feature?), 
a use-case (How would people use your feature?), 
and point out what's the contribution (What will be better with your feature?).
If you are a programmer, you are welcome to implement your feature Idea by your own.
Thus, you should make a fork of the code base and implement your feature.
When your development work is ready and the code is tested an working, merge with the main branch again and send a pull request.
If you have further questions, consider the website \url{http://www.opendiabetes.de}, check the forum at Github or ask a developer on Github.

Data contribution:
Since we are working with machine learning algorithms, we need a lot of (really a massive amount) of data to train and test our algorithms.
If you are willing to spend your data to the project, contact us over the web form on \url{http://www.opendiabetes.de}.
You data will be anonymized, so no personal information about you will be available to the researcher group except Jens Heuschkel, since he will process your data in the first place.
We would be glad to get a message from you! :)
\vspace{1em}

\textbf{Note:} Parts of the plotted findings may be created by big data analysis or machine learning algorithms.
These results should be used with caution.

\textcolor{red}{\textbf{Always talk to your doctor before you change your therapy!}}

\end{changemargin}

\input{tex_g_legendPage}
